### 2020-08-20 manuscript.tex
quantiles linear

\begin{figure}[!h]
\includegraphics[width=\textwidth]{Figures/rateparameterisation.pdf}
\caption{\textbf{Branch rate parameterisations.} Top left: the prior density of a branch rate $r$ under a Log-Normal($-0.5\sigma^2, \sigma$) distribution (with its mean fixed at 1). 
The function for transforming $\mathcal{R}$ into branch rates $r(\mathcal{R})$ is depicted for \textit{real} (top right), \textit{cat} (bottom left), and \textit{quant} (bottom right).
For simplicity there are 10 \textit{cat} bins displayed, however in practice there are $2N-2$ bins. }
\label{fig:rateparams}
\end{figure}

@@

Transforming these quantiles into rates invokes the i-CDF of the underlying \textit{real} clock model distribution:

\begin{align}
r(\mathcal{R}_i) =& \; F^{-1}(\mathcal{R}_i).
\end{align}

However, evaluation of the i-CDF is computationally demanding and this may hinder the performance of the \textit{quant} parameterisation.

While this approach has clear similarities with \textit{cat}, the domain of rates here is continuous (as opposed to being confined to a discrete number of bins).
In this project we extended the family of constant distance operators  \cite{zhang2020improving} so they are compatible with \textit{quant} (\textbf{\nameref{sect:S1Appendix}}).

>>>>

\begin{figure}[!h]
\includegraphics[width=\textwidth]{Figures/rateparameterisation.pdf}
\caption{\textbf{Branch rate parameterisations.} Top left: the prior density of a branch rate $r$ under a Log-Normal($-0.5\sigma^2, \sigma$) distribution (with its mean fixed at 1). 
The function for transforming $\mathcal{R}$ into branch rates $r(\mathcal{R})$ is depicted for \textit{real} (top right), \textit{cat} (bottom left), and \textit{quant} (bottom right).
For visualisation purposes, there are only 10 bins/pieces displayed, however in practice there are $2N-2$ bins for \textit{cat} and 100 pieces for \textit{quant}.
The first and final \textit{quant} pieces are equal to the underlying function however the pieces in between use linear approximations of this function. }
\label{fig:rateparams}
\end{figure}

@@

Transforming these quantiles into rates invokes the i-CDF of the underlying \textit{real} clock model distribution.
However, this function is computationally demanding to evaluate and therefore an approximation of the i-CDF is used:

\begin{align}
r(\mathcal{R}_i) =& \; \hat{F}^{-1}(\mathcal{R}_i)
\end{align}

where $\hat{F}^{-1}$ is a linear piecewise approximation with 100 pieces.
While this approach has clear similarities with \textit{cat}, the domain of rates here is continuous instead of discrete.
In this project we extended the family of constant distance operators  \cite{zhang2020improving} so that they are compatible with \textit{quant}.
Further details on the \textit{quant} piecewise approximation and constant distance operators can be found in \textbf{\nameref{sect:S1Appendix}}.
